---
title: "Rmd Exercise Template"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The question you are answering

You use the `##` to create a header. Use the header to indicate the question you are answering. After the header, in this space here, annotate your answer, telling us what you did.

```{r}
# load data
gapminder <- read.csv(here::here("data/gapminder5.csv"), stringsAsFactors=FALSE)
```

```{r}
# if statement
year <- 2002
if(any(gapminder$year == year)){
   print(paste("Record(s) for the year",year,"found."))
} else {
  print(paste("No records for year",year))
}
```

```{r}
# loop and if statement_1
threshold = mean(gapminder$pop)
for (i in unique(gapminder$country)) {
   country_mean <- mean(gapminder$pop[gapminder$country==i])
   if (country_mean < threshold) {
     mean_le <- mean(gapminder$lifeExp[gapminder$country==i])
     print(paste("Mean Life Expectancy in", i, "is", mean_le))
   } 
}
```
```{r}
# loop and if statement_2
for (i in unique(gapminder$continent)){
    tmp <- mean(gapminder$lifeExp[gapminder$continent==i])
    
    if (tmp < 50){
        print(paste("Average Life Expectancy in", i, "is less than", 50))
    }
    else if (tmp > 50 & tmp < 70){
        print(paste("Average Life Expectancy in", i, "is between", 50, "and", 70))
    }
    else {
        print(paste("Average Life Expectancy in", i, "is greater than", 70))
    }
}

```

```{r}
# Exercise: Write Functions_1
data_col_class <- function(df) {
  for (i in names(df)) {
    print(paste0(i, ": ", mode(df[, i])))
  }
}
data_col_class(gapminder)
```

```{r}
# Exercise: Write Functions_2
mean_and_SD <- function(arr, medianflag=FALSE) { 
    if (medianflag) {print(paste0("Median: ", median(arr)))}
    print(paste0("Mean: ", mean(arr)))
    print(paste0("Standard Deviation: ", sd(arr)))
}
le <- gapminder$lifeExp
mean_and_SD(le, medianflag = F)
mean_and_SD(le, medianflag = T)
```

## Including Plots

You can also embed plots, for example:

```{r}
# Analyzing the relationship_1
plot(log(gapminder$gdpPercap)~log(gapminder$lifeExp))
m <- lm(log(gapminder$gdpPercap)~log(gapminder$lifeExp))
abline(m)

ggplot(aes(x = log(gdpPercap), y = log(lifeExp)), data = gapminder) + geom_point(alpha = 1/2) + geom_smooth(method = 'lm', color = 'red')
```

```{r}
# Analyzing the relationship_2
library(ggthemes)
library(ggplot2)
ggplot(aes(x = log(gdpPercap), y = log(lifeExp)), data = gapminder) + geom_point(alpha = 1/2) + geom_smooth(method = 'lm', color = 'red') + facet_wrap(~gapminder$continent)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
